---
title: "recode_vrs"
author: "Dahham Alsoud"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{recode_vrs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Raison dՐtre
Although new pragmatic platforms currently exist, great deal of research data is still being collected in `excel`, where it is easier to code variables in a `short form`. For example, birth date is commonly coded in a `short form` as "dob" instead of "Date of birth", which is the `publication form`. The same applies to the `levels` of variables, such as "F" and "M", which are both levels for the "Age" variables, and stand for "Female" and "Male", respectively.

Recoding variables and their levels back to their publication form is an inevitable task during statistical analysis and reporting results. 

The function `recode_vrs()` helps effortlessly transform collected data into a publication-ready format using a user-supplied `data dictionary`. Combining `recode_vrs()` with a `data dictionary` ensures `consistency` in recoding across all analyses and publications as one could easily forget how a variable was encoded in a previous analysis or publication. 

## Example
### Making table 1 of raw data
```{r}
library(gtsummary)
data(ibd_data1, package = "phdcocktail")

ibd_data1 |>
  tbl_summary(include = -"patientid")

```

### Making table 1 after recoding
```{r}
library(gtsummary)
library(phdcocktail)

ibd_data_recoded <- recode_vrs(data = ibd_data1, data_dictionary = ibd_data_dict,
vrs = c("disease_location", "disease_behaviour", "gender"), factor = TRUE)

ibd_data_recoded |>
  tbl_summary(include = -"patientid")


```


